% Discussion — framed around practical architectural guidance

\subsection{When Are VQCs Competitive?}

Our results paint a nuanced picture.  On regression tasks with moderate
dimensionality, FC-VQCs can match or exceed strong classical baselines
\emph{while using orders of magnitude fewer parameters}.  This parameter
efficiency is the primary practical advantage of VQCs: on NISQ devices with
limited qubit counts, a 720-parameter FC-VQC is far more deployable than a
13{,}000-parameter MLP.

However, on classification tasks and larger datasets (CA Housing, $n{=}20{,}640$),
gradient-boosted trees remain superior.  This aligns with prior empirical
findings that tree ensembles dominate tabular classification benchmarks, and
suggests that the current advantage of VQCs is concentrated in
\emph{low-parameter regression} settings.

\subsection{The Role of Quantum Attention}

Perhaps our most surprising finding is that quantum self-attention does not
reliably improve performance.  The ablation in Table~\ref{tab:ablation}
shows that FQT \emph{without} attention achieves the highest $R^2$ on Boston
Housing ($0.894$).  We hypothesize two explanations:

\begin{enumerate}
  \item \textbf{Data scale:} Self-attention excels at capturing long-range
    dependencies in sequences.  Tabular datasets with ${\leq}$13 features
    may simply lack the structure that attention is designed to exploit.
  \item \textbf{Optimization difficulty:} The quantum attention mechanism
    introduces additional entangling layers whose gradients may interfere
    with the main VQC parameters, effectively making optimization harder
    without providing representational benefit.
\end{enumerate}

This is a valuable \emph{negative result}: practitioners should not default
to transformer-style VQCs for tabular tasks.  Simpler FC-VQC or ResNet-VQC
architectures are more parameter-efficient and equally or more accurate.

\subsection{Expressibility and Depth Selection}

The expressibility analysis (Appendix~\ref{app:expressibility}) shows that
circuit expressibility saturates at depth~${\approx}\,3$, with KL divergence
dropping from $0.20$ (depth~1) to $0.003$ (depth~3) and plateauing
thereafter.  This has a direct practical implication: \textbf{there is no
benefit to using VQC depths beyond 3} for the \texttt{StronglyEntanglingLayers}
ansatz on 3-qubit circuits.  Deeper circuits add parameters and training
time without accessing additional regions of Hilbert space.

This finding is consistent with the parameter efficiency of FC-VQCs: even
with shallow individual blocks, the multi-layer fully-connected topology
provides sufficient expressiveness through inter-block connectivity rather
than intra-block depth.

\subsection{Practical Architectural Recommendations}

Based on our findings, we offer the following guidance for practitioners:

\begin{itemize}
  \item \textbf{Default choice:} FC-VQC with depth~3 blocks.  Best
    parameter efficiency, competitive accuracy, simplest to train.
  \item \textbf{When you need robustness:} ResNet-VQC.  Skip connections
    stabilize training with minimal parameter overhead.
  \item \textbf{Avoid for tabular data:} Multi-head quantum attention.
    The parameter cost is not justified by accuracy gains at this scale.
  \item \textbf{If using FQT:} Add LayerNorm, especially for classification.
\end{itemize}

\subsection{Limitations}

Our study has several limitations.  All experiments use quantum circuit
simulation; behavior on real hardware with decoherence and gate errors may
differ.  The datasets are small to moderate ($n \leq 20{,}640$) with low
feature dimensionality (${\leq}13$).  Larger, higher-dimensional datasets
may favor different architectures.  Finally, our VQCs use at most 3 qubits
per block; scaling to larger qubit counts could change the relative merits
of the architectures.
% TODO: Add noise robustness discussion after experiments.
