% Related Work

\textbf{Variational quantum circuits.}
VQCs, also known as parameterized quantum circuits (PQCs), have been widely
studied as trainable models for quantum machine
learning~\cite{cerezo2021variational,benedetti2019parameterized}.  Their
expressiveness depends on the circuit ansatz, depth, and entanglement
structure~\cite{schuld2021effect}.  A key challenge is the barren plateau
phenomenon, where gradients vanish exponentially with qubit
count~\cite{mcclean2018barren}, motivating the search for architectures
that train efficiently.

\textbf{Expressibility.}
Sim et al.~\cite{sim2019expressibility} proposed measuring circuit
expressibility via the KL divergence between the fidelity distribution of
random circuit outputs and the Haar-random reference.  This metric has
become a standard tool for comparing ansatz designs.  We use it to
characterize the depth at which our VQC blocks saturate.

\textbf{Quantum transformers.}
Several recent works have explored quantum analogues of the transformer
architecture.  These range from quantum self-attention mechanisms operating
on amplitude-encoded data to fully quantum multi-head attention with
parameterized entangling gates.  Our work differs in providing a controlled
comparison against simpler VQC baselines (FC-VQC, ResNet-VQC) on identical
benchmarks, rather than proposing a new transformer variant in isolation.
% TODO: Add specific citations to quantum transformer papers.

\textbf{Residual connections in quantum circuits.}
Classical residual networks~\cite{he2016deep} inspired several proposals
for skip connections in VQCs, either by adding classical residual paths
around quantum blocks or by using identity-initialized parameterized layers.
Our ResNet-VQC follows the classical residual path approach.

\textbf{Classical baselines for tabular data.}
Gradient-boosted decision trees (XGBoost, CatBoost, LightGBM) consistently
rank among the top methods on tabular benchmarks.  Recent work has
highlighted that deep learning often underperforms tree ensembles on
tabular data, making them an essential baseline for any quantum ML study
claiming practical relevance.
