% Results section — narrative follows the repositioned framing

\input{tables}

\subsection{Main Comparison: Parameter Efficiency of FC-VQCs}
\label{sec:results-main}

Tables~\ref{tab:main-regression} and~\ref{tab:main-classification} present
the main comparison across all architectures and baselines.

On regression tasks, the most striking finding is the \textbf{parameter
efficiency of FC-VQCs}.  On Boston Housing, FC-VQC$_{15\mathrm{t}5\mathrm{t}1}$
achieves $R^2{=}0.889$ with only 720 parameters, outperforming both XGBoost
($0.856$) and CatBoost ($0.861$).  A parameter-matched MLP with 218
parameters reaches only $R^2{=}0.769$, and a full MLP requires
${\sim}$13{,}000 parameters to approach comparable accuracy---a roughly
$18{\times}$ parameter disadvantage.

Quantum Transformer variants (QT, FQT) achieve respectable scores on
CA~Housing ($R^2{\leq}0.814$) and Concrete ($R^2{\leq}0.869$), but at
significantly higher parameter counts (1{,}098--4{,}350) than FC-VQCs
(486--720), and they do not consistently outperform the simpler architectures.
ResNet-VQC provides a reliable middle ground: competitive accuracy with the
same parameter budget as FC-VQC.

On classification (Wine datasets), all quantum models trail tree-based
methods by 6--10\% in accuracy.  This is expected: tabular classification is
a well-known strength of gradient-boosted ensembles.  Among quantum models,
FQT with LayerNorm achieves the highest accuracy ($0.629$ on Wine Red),
suggesting that normalization is particularly important when all operations
are quantum.

\subsection{Multi-Head Attention Scaling}
\label{sec:results-multihead}

Table~\ref{tab:multihead} examines the effect of increasing the number of
attention heads $H$ from 1 to 3 for both QT and FQT.

For QT, increasing $H$ yields mixed results: $H{=}3$ helps on Boston
($0.781 \to 0.834$) but not on Concrete ($0.838 \to 0.837$), while the
parameter count triples ($1{,}380 \to 4{,}350$).  For FQT, multi-head
attention is even less beneficial---$H{=}2$ \emph{degrades} Boston from
$0.799$ to $0.626$.

These results suggest that multi-head quantum attention is not a reliable
way to improve performance on small tabular datasets, and that the added
parameters are poorly utilized.

\subsection{Architecture Ablation: Attention Is Not Always Helpful}
\label{sec:results-ablation}

Table~\ref{tab:ablation} presents ablation experiments removing or modifying
key architectural components.

The most notable finding is that \textbf{removing self-attention from FQT
improves regression accuracy on Boston Housing} ($R^2$: $0.799 \to 0.894$).
This is the highest $R^2$ achieved by any quantum model in our study, and it
comes from a \emph{simpler} architecture.  A similar pattern appears with
Type~3 FFN ($0.885$).  On other datasets the effect is smaller or reversed,
but the overall message is clear: quantum self-attention does not provide a
consistent benefit on tabular data at this scale.

For classification, LayerNorm applied to FQT yields the best quantum
accuracy across the board ($0.629$ on Wine Red, $0.597$ on Wine R+W),
indicating that normalization is important for training stability in fully
quantum architectures.

\subsection{Noise Robustness}
\label{sec:results-noise}

Table~\ref{tab:noise} reports model accuracy under single-qubit depolarizing
noise at strengths $p_d \in \{0.001, 0.005, 0.01, 0.05\}$.

% TODO: Fill in narrative once noise experiments are complete.
% Expected discussion points:
% - Graceful vs. sudden degradation
% - QT vs FQT noise sensitivity differences
% - Implications for near-term hardware deployment
